Seldin Report: Ssec Scores

### 2022-07-12 MSigDB.Rmd
Getting there

all_genes = msigdbr(species = "Rattus norvegicus")

@@

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

tesec_brain = read.csv("TE.Sec_Ssec_brain.csv")
tesec_liver = read.csv("TE.Sec_Ssec_liver.csv")
tensec_brain = read.csv("TE.NSec_Ssec_brain.csv")
tensec_liver = read.csv("TE.NSec_Ssec_liver.csv")
bicor_brain = read.csv("Bicor_brain.csv")
bicor_liver = read.csv("Bicor_liver.csv")

@@

# top 5 TES genes for brain and liver
# the genes theyre correlated to
# convert to entrez ids

# top 5 genes for brain and liver

top.brain = tesec_brain[1:5,]
top.liver = tesec_liver[1:5,]

@@

list.oflists = function(mat)
{
  out = list(c(), c(), c(), c(), c())
  for (i in 1:5)
  {
    save = colnames(mat[,mat[i,] < 0.05])
    out[[i]] = save
  }
  return(out)
}

brain.list = list.oflists(top.corr.brain)
liver.list = list.oflists(top.corr.liver)

combine.brain = unique(c(brain.list[[1]], brain.list[[2]], brain.list[[3]], brain.list[[4]], brain.list[[5]]))

combine.liver = unique(c(liver.list[[1]], liver.list[[2]], liver.list[[3]], liver.list[[4]], liver.list[[5]]))

num.brain = c(length(brain.list[[1]]), length(brain.list[[2]]), length(brain.list[[3]]), length(brain.list[[4]]), length(brain.list[[5]]))

num.liver = c(length(liver.list[[1]]), length(liver.list[[2]]), length(liver.list[[3]]), length(liver.list[[4]]), length(liver.list[[5]]))

@@

get_uniprot = getBM(attributes=c("ensembl_gene_id",
                              "external_gene_name",
                              "description",
                              "chromosome_name",
                              "start_position",
                              "end_position",
                              "gene_biotype",
                            "uniprot_gn_id",
                            "name_1006",
                            "definition_1006","go_linkage_type","namespace_1003"),
                 filters = 'biotype',
                 values = "protein_coding",
                 mart = ensembl)

@@

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
write.csv(entrez_brain.1, "EntrezIds_brain.csv")
write.csv(entrez_liver.1, "EntrezIds_liver.csv")

@@

msigdbr_t2g = all_genes %>% dplyr::distinct(gs_name, entrez_gene) %>% as.data.frame()

@@

# brain.list, liver.list

out.brain = list(c(), c(), c(), c(), c())

for (i in 1:5)
{
  vect = brain.list[[i]]
  entrez = entrez_brain$entrezgene_id[entrez_brain$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = msigdbr_t2g, pAdjustMethod = "fdr")
  out.brain[[i]] = data.frame(ID = listt$ID, Description = listt$Description, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)
}

out.liver = list(c(), c(), c(), c(), c())

for (i in 1:5)
{
  vect = liver.list[[i]]
  entrez = entrez_liver$entrezgene_id[entrez_liver$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = msigdbr_t2g, pAdjustMethod = "fdr")
  out.liver[[i]] = data.frame(ID = listt$ID, Description = listt$Description, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)
}

brain.ids = c(paste(out.brain[[1]]$ID, collapse = ", "), paste(out.brain[[2]]$ID, collapse = ", "), paste(out.brain[[3]]$ID, collapse = ", "), paste(out.brain[[4]]$ID, collapse = ", "), paste(out.brain[[5]]$ID, collapse = ", "))
names(brain.ids) = top.brain[,1]

knitr::kable(brain.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Brain", colnames = "")

liver.ids = c(paste(out.liver[[1]]$ID, collapse = ", "), paste(out.liver[[2]]$ID, collapse = ", "), paste(out.liver[[3]]$ID, collapse = ", "), paste(out.liver[[4]]$ID, collapse = ", "), paste(out.liver[[5]]$ID, collapse = ", "))
names(liver.ids) = top.liver[,1]

knitr::kable(liver.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Liver", colnames = "")

@@

>>>>

H_genes = msigdbr(species = "Rattus norvegicus", category = "H")
C2_genes = msigdbr(species = "Rattus norvegicus", category = "C2") # HAS KEGG genes
C5_genes = msigdbr(species = "Rattus norvegicus", category = "C5") #GO genes
#C8_genes = msigdbr(species = "Rattus norvegicus", category = "C8")

@@

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

tesec_brain = read.csv("Target_TESec_Ssec_brain.csv")
tesec_liver = read.csv("Target_TESec_Ssec_liver.csv")
tensec_brain = read.csv("Target_TENSec_Ssec_brain.csv")
tensec_liver = read.csv("Target_TENSec_Ssec_liver.csv")
bicor_brain = read.csv("Bicor_brain.csv")
bicor_liver = read.csv("Bicor_liver.csv")

@@

# top Ssec genes for brain and liver FROM: SeldinReport_fix.Rmd

top.brain = tesec_brain[1:6,]
top.liver = tesec_liver[1,]

@@

list.oflists = function(mat, num)
{
  out = list(c(), c(), c(), c(), c(), c())
  out = out[1:num]
  if(num > 1)
  {
    for (i in 1:num)
    {
      save = colnames(mat[,mat[i,] < 0.05])
      out[[i]] = save
    }
  }
  else
  {
    save = colnames(mat[,mat[1,] < 0.05])
    out[[1]] = save
  }
  return(out)
}

brain.list = list.oflists(top.corr.brain, nrow(top.brain))
liver.list = list.oflists(top.corr.liver, nrow(top.liver))

combine.brain = unique(c(brain.list[[1]], brain.list[[2]], brain.list[[3]], brain.list[[4]], brain.list[[5]], brain.list[[6]]))

combine.liver = liver.list[[1]]

num.brain = c(length(brain.list[[1]]), length(brain.list[[2]]), length(brain.list[[3]]), length(brain.list[[4]]), length(brain.list[[5]]), length(brain.list[[6]]))

num.liver = c(length(liver.list[[1]]))

@@

@@

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
write.csv(entrez_brain.1, "EntrezIds_brain.csv")
write.csv(entrez_liver.1, "EntrezIds_liver.csv")

@@

msigdbr_t2g_H = H_genes %>% dplyr::distinct(gs_name, entrez_gene) %>% as.data.frame()
msigdbr_t2g_C2 = C2_genes %>% dplyr::distinct(gs_name, entrez_gene) %>% as.data.frame()
msigdbr_t2g_C5 = C5_genes %>% dplyr::distinct(gs_name, entrez_gene) %>% as.data.frame()
#msigdbr_t2g_C8 = C8_genes %>% dplyr::distinct(gs_name, entrez_gene) %>% as.data.frame()

@@

# H

out.brain_H = list(c(), c(), c(), c(), c(), c())
database = msigdbr_t2g_H

for (i in 1:6)
{
  vect = brain.list[[i]]
  entrez = entrez_brain$entrezgene_id[entrez_brain$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
  out.brain_H[[i]] = data.frame(ID = listt$ID, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)
}

out.liver_H = list(c())

  vect = liver.list[[1]]
  entrez = entrez_liver$entrezgene_id[entrez_liver$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
  out.liver_H[[1]] = data.frame(ID = listt$ID, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)

#brain.ids = c(paste(out.brain[[1]]$ID, collapse = ", "), paste(out.brain[[2]]$ID, collapse = ", "), paste(out.brain[[3]]$ID, collapse = ", "), paste(out.brain[[4]]$ID, collapse = ", "), paste(out.brain[[5]]$ID, collapse = ", "))
#names(brain.ids) = top.brain[,1]

#knitr::kable(brain.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Brain", colnames = "")

#liver.ids = c(paste(out.liver[[1]]$ID, collapse = ", "), paste(out.liver[[2]]$ID, collapse = ", "), paste(out.liver[[3]]$ID, collapse = ", "), paste(out.liver[[4]]$ID, collapse = ", "), paste(out.liver[[5]]$ID, collapse = ", "))
#names(liver.ids) = top.liver[,1]

#knitr::kable(liver.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Liver", colnames = "")

# C2

out.brain_C2 = list(c(), c(), c(), c(), c(), c())
database = msigdbr_t2g_C2

for (i in 1:6)
{
  vect = brain.list[[i]]
  entrez = entrez_brain$entrezgene_id[entrez_brain$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
  out.brain_C2[[i]] = data.frame(ID = listt$ID, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)
}

out.liver_C2 = list(c())

  vect = liver.list[[1]]
  entrez = entrez_liver$entrezgene_id[entrez_liver$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
  out.liver_C2[[1]] = data.frame(ID = listt$ID, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)

#brain.ids = c(paste(out.brain[[1]]$ID, collapse = ", "), paste(out.brain[[2]]$ID, collapse = ", "), paste(out.brain[[3]]$ID, collapse = ", "), paste(out.brain[[4]]$ID, collapse = ", "), paste(out.brain[[5]]$ID, collapse = ", "))
#names(brain.ids) = top.brain[,1]

#knitr::kable(brain.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Brain", colnames = "")

#liver.ids = c(paste(out.liver[[1]]$ID, collapse = ", "), paste(out.liver[[2]]$ID, collapse = ", "), paste(out.liver[[3]]$ID, collapse = ", "), paste(out.liver[[4]]$ID, collapse = ", "), paste(out.liver[[5]]$ID, collapse = ", "))
#names(liver.ids) = top.liver[,1]

#knitr::kable(liver.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Liver", colnames = "")

# C5

out.brain_C5 = list(c(), c(), c(), c(), c(), c())
database = msigdbr_t2g_C5

for (i in 1:6)
{
  vect = brain.list[[i]]
  entrez = entrez_brain$entrezgene_id[entrez_brain$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
  out.brain_C5[[i]] = data.frame(ID = listt$ID, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)
}

out.liver_C5 = list(c())

  vect = liver.list[[1]]
  entrez = entrez_liver$entrezgene_id[entrez_liver$ensembl_gene_id %in% vect]
  entrez = na.omit(entrez)
  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
  out.liver_C5[[1]] = data.frame(ID = listt$ID, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = listt$geneID)

#brain.ids = c(paste(out.brain[[1]]$ID, collapse = ", "), paste(out.brain[[2]]$ID, collapse = ", "), paste(out.brain[[3]]$ID, collapse = ", "), paste(out.brain[[4]]$ID, collapse = ", "), paste(out.brain[[5]]$ID, collapse = ", "))
#names(brain.ids) = top.brain[,1]

#knitr::kable(brain.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Brain", colnames = "")

#liver.ids = c(paste(out.liver[[1]]$ID, collapse = ", "), paste(out.liver[[2]]$ID, collapse = ", "), paste(out.liver[[3]]$ID, collapse = ", "), paste(out.liver[[4]]$ID, collapse = ", "), paste(out.liver[[5]]$ID, collapse = ", "))
#names(liver.ids) = top.liver[,1]

#knitr::kable(liver.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Liver", colnames = "")

# C8

#out.brain_C8 = list(c(), c(), c(), c(), c())
#database = msigdbr_t2g_C8

#for (i in 1:5)
#{
#  vect = brain.list[[i]]
#  entrez = entrez_brain$entrezgene_id[entrez_brain$ensembl_gene_id %in% vect]
#  entrez = na.omit(entrez)
#  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
#  out.brain_C8[[i]] = data.frame(ID = listt$ID, Description = #listt$Description, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = #listt$geneID)
#}

#out.liver_C8 = list(c(), c(), c(), c(), c())

#for (i in 1:5)
#{
#  vect = liver.list[[i]]
#  entrez = entrez_liver$entrezgene_id[entrez_liver$ensembl_gene_id %in% vect]
#  entrez = na.omit(entrez)
#  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
#  out.liver_C8[[i]] = data.frame(ID = listt$ID, Description = #listt$Description, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = #listt$geneID)
#}

#brain.ids = c(paste(out.brain[[1]]$ID, collapse = ", "), paste(out.brain[[2]]$ID, collapse = ", "), paste(out.brain[[3]]$ID, collapse = ", "), paste(out.brain[[4]]$ID, collapse = ", "), paste(out.brain[[5]]$ID, collapse = ", "))
#names(brain.ids) = top.brain[,1]

#knitr::kable(brain.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Brain", colnames = "")

#liver.ids = c(paste(out.liver[[1]]$ID, collapse = ", "), paste(out.liver[[2]]$ID, collapse = ", "), paste(out.liver[[3]]$ID, collapse = ", "), paste(out.liver[[4]]$ID, collapse = ", "), paste(out.liver[[5]]$ID, collapse = ", "))
#names(liver.ids) = top.liver[,1]

#knitr::kable(liver.ids, caption = "Enrichment of Target Liver Genes Influenced by TES Protein-Coding Genes from the Liver", colnames = "")

#first.brain = rbind(out.brain_H[[1]], out.brain_C2[[1]], out.brain_C5[[1]], out.brain_C8[[1]])
#second.brain = rbind(out.brain_H[[2]], out.brain_C2[[2]], out.brain_C5[[2]], out.brain_C8[[2]])
#third.brain = rbind(out.brain_H[[3]], out.brain_C2[[3]], out.brain_C5[[3]], out.brain_C8[[3]])
#fourth.brain = rbind(out.brain_H[[4]], out.brain_C2[[4]], out.brain_C5[[4]], out.brain_C8[[4]])
#fifth.brain = rbind(out.brain_H[[5]], out.brain_C2[[5]], out.brain_C5[[5]], out.brain_C8[[5]])

#first.liver = rbind(out.liver_H[[1]], out.liver_C2[[1]], out.liver_C5[[1]], out.liver_C8[[1]])
#second.liver = rbind(out.liver_H[[2]], out.liver_C2[[2]], out.liver_C5[[2]], out.liver_C8[[2]])
#third.liver = rbind(out.liver_H[[3]], out.liver_C2[[3]], out.liver_C5[[3]], out.liver_C8[[3]])
#fourth.liver = rbind(out.liver_H[[4]], out.liver_C2[[4]], out.liver_C5[[4]], out.liver_C8[[4]])
#fifth.liver = rbind(out.liver_H[[5]], out.liver_C2[[5]], out.liver_C5[[5]], out.liver_C8[[5]])

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
#write.csv(first.brain, "Brain Enrichment_1.csv")
#write.csv(second.brain, "Brain Enrichment_2.csv")
#write.csv(third.brain, "Brain Enrichment_3.csv")
#write.csv(fourth.brain, "Brain Enrichment_4.csv")
#write.csv(fifth.brain, "Brain Enrichment_5.csv")

#write.csv(first.liver, "liver Enrichment_1.csv")
#write.csv(second.liver, "liver Enrichment_2.csv")
#write.csv(third.liver, "liver Enrichment_3.csv")
#write.csv(fourth.liver, "liver Enrichment_4.csv")
#write.csv(fifth.liver, "liver Enrichment_5.csv")

@@

### Enrichment of Target Liver Protein-Coding Genes acted upon by TES Protein-Coding Genes from Brain

#### HALLMARK GENE SET

knitr::kable(out.brain_H[[1]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_H[[2]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000002548")
knitr::kable(out.brain_H[[3]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000002381")
knitr::kable(out.brain_H[[4]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_H[[5]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_H[[6]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000000010")

#### C2 GENE SET

```{r, echo = FALSE}
# Search KEGG

these_1 = grep("KEGG", out.brain_C2[[1]][,1], value = TRUE)
these_2 = grep("KEGG", out.brain_C2[[2]][,1], value = TRUE)
these_3 = grep("KEGG", out.brain_C2[[3]][,1], value = TRUE)
these_4 = grep("KEGG", out.brain_C2[[4]][,1], value = TRUE)
these_5 = grep("KEGG", out.brain_C2[[5]][,1], value = TRUE)
these_6 = grep("KEGG", out.brain_C2[[6]][,1], value = TRUE)

knitr::kable(out.brain_C2[[1]][out.brain_C2[[1]][,1] %in% these_1,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_C2[[2]][out.brain_C2[[2]][,1] %in% these_2,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000002548")
knitr::kable(out.brain_C2[[3]][out.brain_C2[[3]][,1] %in% these_3,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000002381")
knitr::kable(out.brain_C2[[4]][out.brain_C2[[4]][,1] %in% these_4,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_C2[[5]][out.brain_C2[[5]][,1] %in% these_5,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_C2[[6]][out.brain_C2[[6]][,1] %in% these_6,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000000010")

#### C5 GENE SET

these_1 = grep("GOBP", out.brain_C5[[1]][,1], value = TRUE)
these_2 = grep("GOBP", out.brain_C5[[2]][,1], value = TRUE)
these_3 = grep("GOBP", out.brain_C5[[3]][,1], value = TRUE)
these_4 = grep("GOBP", out.brain_C5[[4]][,1], value = TRUE)
these_5 = grep("GOBP", out.brain_C5[[5]][,1], value = TRUE)
these_6 = grep("GOBP", out.brain_C5[[6]][,1], value = TRUE)

knitr::kable(out.brain_C5[[1]][out.brain_C5[[1]][,1] %in% these_1,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_C5[[2]][out.brain_C5[[2]][,1] %in% these_2,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000002548")
knitr::kable(out.brain_C5[[3]][out.brain_C5[[3]][,1] %in% these_3,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000002381")
knitr::kable(out.brain_C5[[4]][out.brain_C5[[4]][,1] %in% these_4,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_C5[[5]][out.brain_C5[[5]][,1] %in% these_5,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_C5[[6]][out.brain_C5[[6]][,1] %in% these_6,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000000010")

### Enrichment of Target Brain Protein-Coding Genes acted upon by TES Protein-Coding Genes from Liver

#### HALLMARK GENE SET

knitr::kable(out.liver_H[[1]], caption = "Hallmark Liver TES Protein-Coding Gene: ENSRNOG00000047481")

#### C2 GENE SET

```{r, echo = FALSE}
# search KEGG

these_1 = grep("KEGG", out.liver_C2[[1]][,1], value = TRUE)

knitr::kable(out.liver_C2[[1]][out.liver_C2[[1]][,1] %in% these_1,], caption = "C2: KEGG Liver TES Protein-Coding Gene: ENSRNOG00000047481")

#### C5 GENE SET

these_1 = grep("GOBP", out.liver_C5[[1]][,1], value = TRUE)

knitr::kable(out.liver_C5[[1]][out.liver_C5[[1]][,1] %in% these_1,], caption = "C5: GO Biological Processes Liver TES Protein-Coding Gene: ENSRNOG00000047481")

### 2022-07-12 Partial Correlation Ssec Values.Rmd
Getting there

## DATA
setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

@@

## TES BRAIN ##

target_liver = cbind(tes.liver, tens.liver) #merge instead
target_liver = target_liver[rownames(tes.brain),]

## TES LIVER ##

@@

@@

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

#write.csv(pacor.ssec.brain.fin, "TES_PaCor_Ssec_brain.csv")
#write.csv(pacor.ssec.liver.fin, "TES_PaCor_Ssec_liver.csv")
write.csv(corr.pacorssec.brain, "Pacor_Brain_TES.csv")
write.csv(corr.pacorssec.liver, "Pacor_Liver_TES.csv")
write.csv(pval.pacorssec.brain, "Pacor.pval_Brain_TES.csv")
write.csv(pval.pacorssec.liver, "Pacor.pval_Liver_TES.csv")

@@

## TENS BRAIN ##

@@

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

#write.csv(pacor.tens.ssec.brain.fin, "TENS_PaCor_Ssec_brain.csv")
write.csv(pacor.tens.ssec.liver.fin, "TENS_PaCor_Ssec_liver.csv")

@@

>>>>

## DATA
#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

@@

target_liver = cbind(tes.liver, tens.liver) 
target_liver = target_liver[rownames(tes.brain),]

@@

partial.correlation = function(x, y)
{
  test = data.frame(x, y)
  estimate = ggm.estimate.pcor(test, method = "static") 
  edge = network.test.edges(estimate)

  this = edge[edge$node1 == 1,]
  score = sum(-log(this$pval))/length(y)

  return(score)

}

pacor.ssec.brain = apply(tes.brain, 2, partial.correlation, y = target_liver)
pacor.ssec.liver = apply(tes.liver, 2, partial.correlation, y = target_brain)

@@

write.csv(pacor.ssec.brain.fin, "TES_PaCor_Ssec_brain.csv")
write.csv(pacor.ssec.liver.fin, "TES_PaCor_Ssec_liver.csv")
#write.csv(corr.pacorssec.brain, "Pacor_Brain_TES.csv")
#write.csv(corr.pacorssec.liver, "Pacor_Liver_TES.csv")
#write.csv(pval.pacorssec.brain, "Pacor.pval_Brain_TES.csv")
#write.csv(pval.pacorssec.liver, "Pacor.pval_Liver_TES.csv")

@@

pacor.tens.ssec.brain = apply(tens.brain, 2, partial.correlation, y = target_liver)
pacor.tens.ssec.liver = apply(tens.liver, 2, partial.correlation, y = target_brain)

@@

write.csv(pacor.tens.ssec.brain.fin, "TENS_PaCor_Ssec_brain.csv")
write.csv(pacor.tens.ssec.liver.fin, "TENS_PaCor_Ssec_liver.csv")

@@

target_liver = cbind(tes.liver, tens.liver) 
target_liver = target_liver[rownames(tes.brain),]

setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

write.csv(corr.pacorssec.brain, "Pacor_Brain_TES.csv")
write.csv(corr.pacorssec.liver, "Pacor_Liver_TES.csv")
write.csv(pval.pacorssec.brain, "Pacor.pval_Brain_TES.csv")
write.csv(pval.pacorssec.liver, "Pacor.pval_Liver_TES.csv")

############################################################

### 2022-07-12 SeldinReport.Rmd
Getting there

## Comparing Tissue-Specific Secreted to Tissue-Specific Non-Secreted with reference group All Target Genes

```{r, echo = FALSE, message = FALSE}
# Calculate Ssec values: tissue-specific -> full
#### TS ####
## BRAIN ##

@@

@@

```{r, echo = FALSE, message = FALSE}
# Calculate Ssec values: tissue-specific -> ns tissue-specific
#### TS ####
## BRAIN ##
target_liver = cbind(ts_protein_liver, tsns_protein_liver)

@@

write.csv(ts_Ssec_brain, "Target_TESec_Ssec_brain.csv")
write.csv(ts_Ssec_liver, "Target_TESec_Ssec_liver.csv")
write.csv(tsns_Ssec_brain, "Target_TENSec_Ssec_brain.csv")
write.csv(tsns_Ssec_liver, "Target_TENSec_Ssec_liver.csv")

@@

with(compare.b, qqplot(val[trt == "TSNS brain"], val[trt == "TSS brain"]))
abline(a = 0, b = 1)

@@

with(compare.l, qqplot(val[trt == "TSNS liver"], val[trt == "TSS liver"]))
abline(a = 0, b = 1)

@@

```{r}
# checking secreted

@@

```{r}
# annotation

@@

```{r, echo = FALSE, warning = FALSE}

@@

# still want to compare protein_brain, protein_liver- server

@@

```
# compare secreted to non-secreted

```{r}

@@

```{r}

>>>>

```{r, echo = FALSE, message = FALSE, eval = FALSE}
## Comparing Tissue-Specific Secreted to Tissue-Specific Non-Secreted with reference group All Target Genes

# Calculate Ssec values: tissue-specific -> full
#### TS ####
## BRAIN ##

@@

```{r, echo = FALSE, eval = FALSE}
# Visualizations
#hist(Ssec_brain$Ssec)
#hist(ts_Ssec_brain$Ssec)

@@

```{r, echo = FALSE, message = FALSE}
# Calculate Ssec values: tissue-specific -> s tissue-specific
#### TS ####
## BRAIN ##
target_liver = cbind(ts_protein_liver, tsns_protein_liver)
target_liver = target_liver[rownames(ts_protein_brain),]

@@

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

#write.csv(ts_Ssec_brain, "Target_TESec_Ssec_brain.csv")
#write.csv(ts_Ssec_liver, "Target_TESec_Ssec_liver.csv")
#write.csv(tsns_Ssec_brain, "Target_TENSec_Ssec_brain.csv")
#write.csv(tsns_Ssec_liver, "Target_TENSec_Ssec_liver.csv")

@@

#with(compare.b, qqplot(val[trt == "TSNS brain"], val[trt == "TSS brain"]))
#abline(a = 0, b = 1)

@@

#with(compare.l, qqplot(val[trt == "TSNS liver"], val[trt == "TSS liver"]))
#abline(a = 0, b = 1)

## BRAIN

with(this, qqplot(val[trt == "Not Secreted"], val[trt == "Secreted"], xlab = "Not Secreted", ylab = "Secreted", main = "QQ Plot for Brain Proteins"))
abline(a = 0, b = 1)

## LIVER

sec = ts_Ssec_liver$Ssec
nsec = tsns_Ssec_liver$Ssec

with(this, qqplot(val[trt == "Not Secreted"], val[trt == "Secreted"], xlab = "Not Secreted", ylab = "Secreted", main = "QQ Plot for Liver Proteins"))
abline(a = 0, b = 1)

@@

```{r, eval = FALSE, echo = FALSE}
# checking secreted

@@

```{r, echo = FALSE, eval = FALSE}
# annotation

@@

```{r, echo = FALSE, warning = FALSE, eval = FALSE}

@@

```{r, echo = FALSE, eval = FALSE}

@@

# compare secreted to non-secreted

```{r, echo = FALSE, eval = FALSE}

@@

```{r, echo = FALSE, eval = FALSE}
